\documentclass[runningheads,a4paper]{llncs}

% Packages
\usepackage{amssymb}
\setcounter{tocdepth}{3}
% Our packages
\usepackage{graphicx} % Deal with images
\usepackage[utf8]{inputenc} % Provide special ponctuations
\usepackage{subcaption}
\captionsetup{compatibility=false}
\renewcommand{\thesubfigure}{\roman{subfigure}}
\usepackage{paralist}
\usepackage{url}
\usepackage{amsmath}
% Algorithm
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\algrenewcommand\Return{\State \algorithmicreturn{} }
\algnewcommand{\LineComment}[1]{\State \(\triangleright\) #1}

%% Emails
%\urldef{\mailsa}\path|{butz,dossantos,oliveira}@cs.uregina.ca|
\urldef{\mailsa}\path|{author1,author2,author2}@institute1|
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\begin{document}

% Title
\mainmatter
\title{On Theoretical Properties of \\ Augmented Sum Product Networks}
\titlerunning{On Theoretical Properties of \\ Augmented Sum Product Networks}

%% Authors
%\author{
%Andr\'e E. dos Santos\inst{1} 
%\and
%Cory J. Butz\inst{1} 
%\and 
%Jhonatan S. Oliveira\inst{1} 
%}
% Authors
\author{
Author 1\inst{1} 
\and
Author 2\inst{1} 
\and 
Author 3\inst{1} 
}
\authorrunning{On The Conversion of Augmented Sum Product Networks to Bayesian Networks}

% Institution
%\institute{
%Department of Computer Science, University of Regina, Canada\\
%\mailsa\\
%}
\institute{
Department 1, Institute 1, Country 1\\
\mailsa\\
}

% Print title
\toctitle{On The Conversion of Augmented Sum Product Networks to Bayesian Networks}
\tocauthor{On The Conversion of Augmented Sum Product Networks to Bayesian Networks}
\maketitle


% Abstract

\begin{abstract}
\emph{Sum-Product Network} (SPN) is probabilistic graphical model that also benefits from the properties of deep learning models.
%In an SPN, leaf nodes are indicators over Boolean variables and the remaining variables are either sum or product nodes.
The main feature in SPNs is that inference is linear with respect to the size of the network when certain constrains are satisfied.
There are two methods in the literature to convert an SPN to a \emph{Bayesian Network} (BN).
The first method applies the conversion of SPNs into BNs using algebraic decision diagrams to represent the local conditional probability distributions.
The second method is given by the theoretical foundation for latent variable interpretation in augmented SPNs.
In this paper we propose a method for conversion of augmented SPN to BNs.
Our method can convert augmented SPNs to BNs preserving the dependencies among random variables and latent variables.
%The introduced nodes in an augmented SPN is dealt without 
As results, we establish a common ground between the current methods for converting SPNs to BNs.
We also propose an method for augmenting an SPN that requires less modifications on the graph.
Our work continues to give a broader perspective of probabilistic semantics implied by the structure of an SPN through generated the BN.
\end{abstract}

\keywords{sum product networks, conditional independence, deep learning}


% Sections
\input{sections/introduction}
\input{sections/background}
\input{sections/aug_spns}
\input{sections/advantages}
\input{sections/conclusion}

% References
\bibliographystyle{splncs03}
\bibliography{references/references}

\end{document}
